\documentclass[11pt,a4paper]{article}
\usepackage{styles} % Imports stylesheet 
\usepackage[utf8x]{inputenc}
\usepackage[pdftex]{graphicx} % Required for including pictures
\usepackage[pdftex,linkcolor=black,pdfborder={0 0 0}]{hyperref} % Format links for pdf
\usepackage{calc} % To reset the counter in the document after title page
\usepackage{enumitem} % Includes lists
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\frenchspacing % No double spacing between sentences

\usepackage[a4paper, lmargin=0.1666\paperwidth, rmargin=0.1666\paperwidth, tmargin=0.1111\paperheight, bmargin=0.1111\paperheight]{geometry} %margins
%\usepackage{parskip}

\usepackage[all]{nowidow} % Tries to remove widows
\usepackage[protrusion=true,expansion=true]{microtype} % Improves typography, load after fontpackage is selected

%-----------------------
% Set pdf information and add title, fill in the fields
%-----------------------
\hypersetup{ 	
pdfsubject = {},
pdftitle = {},
pdfauthor = {}
}

%-----------------------
% Begin document
%-----------------------
\begin{document} 
\section*{\LARGE{Thomas Bishop}}
\subsection*{\Large{Web developer}}

Highly motivated independent frontend web developer and technical SEO consultant committed to building clean, efficient and performant websites and storefronts.

\begin{itemize}
    \item \href{https://www.thomas-bishop.co.uk}{thomas-bishop.co.uk}
    \item \href{mailto:thomas@thomas-bishop.com}{thomas@thomas-bishop.com}
    \item  \href{https://www.google.com/maps/place/Peacehaven/@50.7980857,-0.0088727,14z/data=!3m1!4b1!4m5!3m4!1s0x47df7d76d09003cd:0x2d61228cfd5cf235!8m2!3d50.793209!4d-0.005174}{Peacehaven, East Sussex}
\end{itemize}

\section*{Technical skills}
\begin{itemize}
    \item \textbf{Languages:} JavaScript, HTML5, CSS3, LaTeX, Liquid
    \item \textbf{Build tools:} Git, CLI, (Bash/Zsh), Node.js, Yarn, npm, Gulp, Webpack, SSH, Netlify, Heroku, Lighthouse
    \item \textbf{Frameworks and libraries}  Material, Bootstrap 4, Bulma, Gatsby.js, Jekyll, Vue.js
    \item \textbf{Content management systems:} WordPress, Drupal (basic) 
    \item \textbf{Data:} MySQL, JSON, Cube.js 
\end{itemize}  

\section*{Experience}
\subsection*{Freelance client work}
\subsubsection*{Remote web developer | \href{https://www.clareshort.org}{clareshort.org} | 2016 --- present }
\begin{itemize}
    \item Clare Short is the UK's former Secretary of State for International Development.
    \item Developed, designed and now maintain \href{https://www.clareshort.org}{clareshort.org} as a responsive WordPress.org website.
    \item In addition to ongoing maintenance and content manangement I provide technical SEO services.
\end{itemize}

\subsubsection*{Remote web developer | University of Sussex | June---July 2019  }
\begin{itemize}
    \item Hired by the University's Digital Humanities Lab to make customisations to the \href{http://makingafricanconnections.org/s/archive/page/index}{Making African Connections Digital Archive}
    \item Introduced several front-end refinements to make the site responsive and ensure functionality not compromised on 2G African networks.
    \item Implemented backend processes to assist researchers in showcasing artefacts.
\end{itemize}

\subsubsection*{Remote web developer | \href{https://www.clareshort.org}{Modish Living} | 2019 --- present }
\begin{itemize}
    \item Modish Living is a reclaimed furniture retailer located in Hove, East Sussex. 
    \item Implemented a redesign of their Shopify site and to introduce several custom features that were lacking in previous iterations of the site, including:
        \begin{itemize}
            \item a graphical page builder to allow content managers to easily add content blocks and control layout and placement
            \item a custom 'mega navigation' that enabled in-menu promotions
            \item the introduction of a 3D product image rotator
            \item streamlining the aggregration and compression of high-resolution product-images with a modern pipeline
        \end{itemize}
    \item I now maintain the site on a retainer basis   
\end{itemize}

\subsubsection*{Remote web developer | Colour Me KT | 2019 --- present }
\begin{itemize}
    \item Refurbished and upscaled furniture store with Shopify e-commerce site.
    \item Managed domain migration from Etsy/Facebook to a dedicated Shopify store that integrates the different product lines and selling channels
    \item Made numerous front end alterations to the site and built new templates for curated blog and product content
    \item Conducted a detailed technical SEO audit of the site, implementing the recommendations myself
    \item I now maintain the site on a retainer basis
\end{itemize}

\subsection*{Salaried work}

\subsubsection*{Technical SEO analyst | \href{https://www.rocketmill.co.uk/}{RocketMill} | 2017-18 }
\begin{itemize}
    \item Managed several client accounts as chief SEO manager: Dropbox, \emph{Financial Times}, Kimberley Clark.
    \item Through regular technical auditing, competitor and link analyses, forecasting and data review I was able to help clients solve technical search issues and drive market performance.
\end{itemize}

\subsubsection*{SEO analyst | \href{https://obaninternational.com/}{Oban International | 2017} }
\begin{itemize}
    \item Joined Oban as a developer with limited SEO experience. Underwent six-month training programme to assimilate the core principles and procedures of SEO, with a specific focus on international markets and technologies.
    \item Contributed to the SEO management of a range of client accounts including the BBC World Service, Camper, and AXA Healthcare Insurance.
    \item Learned how search engines and ranking algorithms work outside of the Google sphere, i.e Yandax, Baidu, Naver etc.
\end{itemize}

\subsection*{Teaching}
    \begin{itemize}
        \item Qualified as a primary school teacher in 2012. Passed professional induction in 2013.
        \item Worked as a teacher in a number of schools throughout South London, mainly teaching Years 4 and 5.
    \end{itemize}
\section*{Education}
\textbf{Postgraduate Certificate of Education}, Middlesex University (2011---12) \\
\textbf{B. A Philosophy}, University of Warwick (2006---2009), graduated 2:1



\end{document}